Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-02-01 manuscript/draft_rsfmri.Rmd
merged into branch and solved conflicts

#### Functional Quality control
Resting state fMRI data quality control was performed according to the protocol by @Ciric_2018.
As the expected average head motion was high in this sample, it was difficult to determine an appropriate exclusion threshold which would not lead to the exclusion of a high number of individuals [@Beyer_2020]. Thus, we did not exclude any participants based on mean framewise displacement (FD) estimates beyond those who failed the anatomical preprocessing. We applied best-practice motion correction (ICA-AROMA and CC, plus optionally GSR) and monitored the reduction of motion-related artifact according to current recommendations [@Ciric_2018]. In addition, for models showing a significant time-by-group interaction, we performed a sensitivity analysis excluding the 10% data sets with highest mean FD (mFD).
```{r carpetplot, out.width="49%", out.height="30%", fig.cap="Carpet plot for quality control", fig.subcap=c("Example 1 with strong amount of structured noise", "Example 2 with less amount of structured noise"), fig.show='hold',fig.align='center', echo=FALSE}
carpets=c("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/carpetplotadi006fu2.jpeg","/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/carpetplotadi16fu.jpeg")
knitr::include_graphics(carpets)
```
On the single-subject level, we used `plot_carpet` from `niworkflows.viz.plots` to generate carpet plots which depict denoising quality. Figure \@ref(fig:carpetplot) shows an exemplary carpet plot with (from top to bottom): percent outliers defined by AFNI, mFD, `OutlierCount`, DVARS (spatial root mean square of the data after temporal differencing),voxelwise timeseries from minimally preprocessed, AROMA non-aggressive and aggressive denoising, CC and CC + GSR data (red: GM voxels, green: WM voxels, blue: ventricle, green: cerebellum). All carpet plots were visually checked and if there was still structured noise in the CC+GSR-denoised functional data (such as black/white stripes, signal dropout), the participant was given a rating of 1 in `QA residuals`.
We evaluated mFD-FC relationships by computing a functional connectome based on [@Power_2012]. In more detail, we used the MNI coordinates of 246 cortical and subcortical spherical seed regions with 5mm radius in `NiftiSpheresMasker`, and calculated the Spearman rank correlation between these time series. Then, we correlated mean FD and QC values for each node across participants, and plotted the resulting mFD-FC correlation values in histogram (see Figure \@ref{exampleFC}. We reported the mFD-FC correlation per preprocessing scheme.
Further, we evaluated the distance-dependence of mFD-FC correlations by correlating the euclidean distance between nodes with the mFD-QC correlation and report mean, median and standard deviations of mFD, DVARS and number of outliers over all participants.

@@

```{r calculate summary of QA, eval=TRUE, echo=FALSE}
for (i in 1:nrow(final)) {
  tmp = strsplit(toString(final[i, "scan_dir"]), '/')[[1]][8]
  conf = read.csv(
    paste0("/data/pt_02161/preprocessed/resting/detailedQA/metrics/",
      tmp, "/confounds.csv"))
  tmp = cor.test(conf$DVARS, conf$FD)
  final[i, "corr_DVARS_FD"] = tmp$estimate
  final[i, "mean_DVARS"] = mean(conf$DVARS, na.rm = TRUE)
  final[i, "max_DVARS"] = max(conf$DVARS, na.rm = TRUE)
  final
}
write.csv(file = "report/all_QA_measures.csv", final)

@@

```{r prepare tsnr ROI plot, eval=TRUE}
final$subj.ID_tp=paste0(final$subj.ID,'_', final$tp)

tsnr=read.table("/data/pt_02161/Analysis/Preprocessing/qa/rs_qa/group_level_QA/check_tsnr/tsnr_in_ROIs.txt")
tsnr=tsnr[tsnr$V1!="subj",]
colnames(tsnr)=c("subj.ID_tp","roi","median","mean","sd")
levels(tsnr$roi)=droplevels(tsnr$roi)
levels(tsnr$roi)=c("NAcc", "PCC/precuneus")
tsnr$mean=as.double(tsnr$mean)

final_tsnr=merge(final, tsnr, by="subj.ID_tp", all.x=TRUE)

p<-ggplot(aes(as.factor(roi), mean),data=final_tsnr) +
  geom_violin(aes(fill=roi), alpha=0.5) + geom_jitter(height = 0, width = 0.1) + xlab("Region of interest") + ylab("average tSNR") +
  scale_fill_manual(values=wes_palette("Darjeeling2",5,type="discrete")[2:3]) +
  theme(axis.text=element_text(size=10),
  axis.title=element_text(size=12),
  strip.text = element_text(size=12),
  legend.position="")
ggsave("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/tsnr.jpeg", height = 6.604, units="cm", p)
```

@@

#networks=c("./report/DMN_thresholded_for_clusterFWE005.png","./report/Rew_thresholded_for_clusterFWE005.png")
networks=c("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/DMN_thresholded_for_clusterFWE005.png", "/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/Rew_thresholded_for_clusterFWE005.png")
tsnr=c("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/tsnr.jpeg")
```
```{r figDvarsmFD, fig.align = "center", out.width="100%", fig.cap='Summary of quality measures DVARS and mFD', echo=FALSE}
figList <- readRDS(file = "../report/fig/figDvarsmFDList.rds")
(figList$fig1 | figList$fig2) / figList$fig3
```

```{r figNetworks, echo=FALSE, out.width="49%", out.height="30%", fig.cap="Resting state networks based on AROMA+CC+GSR input data, one-sample t-tests adjusting for age and sex over all timepoints and participants with bootstrapped clusterwise inference (p FWE<0.05)", fig.subcap=c("DMN seeded from precuneus", "Reward network seeded from Nucleus Accumbens"),fig.show='hold',fig.align='center'}
networks = c("../report/fig/DMN_thresholded_for_clusterFWE005.pdf",
             "../report/fig/Rew_thresholded_for_clusterFWE005.pdf")
knitr::include_graphics(networks)
knitr::include_graphics(tsnr)
```

@@

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="40%",  eval=FALSE}
readRDS(file = "../report/fig/fig_tSNR.rds")
```

@@

final_FC <- read.csv("../report/final_FC.csv")

agg_FC_DMN=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/DMN/agg_FC_DMN.txt")
agg_FC_DMN_ID=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/DMN/agg_FC_DMN_ID.txt")
agg_FC_Rew_ID=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/Rew/agg_FC_Rew_ID.txt")
agg_FC_Rew=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/Rew/agg_FC_Rew.txt")
for (i in c(1:nrow(agg_FC_DMN_ID))){
  agg_FC_Rew[i,"subj.ID_tp"]=strsplit(base::strsplit(as.character(agg_FC_Rew_ID[i,"V1"]),'/')[[1]][10],'_nacc')[[1]][1]
  agg_FC_DMN[i,"subj.ID_tp"]=strsplit(base::strsplit(as.character(agg_FC_DMN_ID[i,"V1"]),'/')[[1]][10],'_pcc')[[1]][1]
}

colnames(agg_FC_Rew)=c("mean_Rew_conn","sd_Rew_conn","subj.ID_tp")
colnames(agg_FC_DMN)=c("mean_DMN_conn","sd_DMN_conn","subj.ID_tp")

final_FC=merge(final, agg_FC_Rew, by="subj.ID_tp", all.x=TRUE)
final_FC=merge(final_FC, agg_FC_DMN, by="subj.ID_tp", all.x=TRUE)
final_FC$subj.ID=as.factor(final_FC$subj.ID)
final_FC$group_factor=relevel(final_FC$group_factor, ref = "KG")

#calculate mean BMI over timepoints
final_FC.meanBMI=tapply(X=final_FC$BMI,
                        INDEX=final_FC$subj.ID, FUN=mean, na.rm=TRUE)
final_FC$mean.BMI=
  final_FC.meanBMI[as.numeric(final_FC$subj.ID)]
final_FC$within.BMI=
  final_FC$BMI-final_FC$mean.BMI

#calculate mean FD over timepoints
final_FC.meanFD=tapply(X=final_FC$logmFD,
                        INDEX=final_FC$subj.ID, FUN=mean, na.rm=TRUE)
final_FC$mean.logmFD=
  final_FC.meanFD[as.numeric(final_FC$subj.ID)]
final_FC$within.logmFD=
  final_FC$logmFD-final_FC$mean.logmFD

```
```{r figaggDMN, fig.cap="DMN connectivity per group over time", out.width="75%", echo=FALSE}
fig_DMNconn<-mk_figDMNdescr(final_FC)
fig_DMNconn
```
```{r figaggRew,fig.cap="Reward network connectivity per group over time", out.width="75%", echo=FALSE}
fig_Rewconn<-mk_figRewdescr(final_FC)
fig_Rewconn
```

@@

```{r figDMNconn, echo=FALSE}
readRDS(file = "../report/fig/figDMNconn.rds")
```

@@

R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +  (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tp=anova(R1,R0)
```
```{qa check Rew model age,sex, echo=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

```{r figRewconn, echo=FALSE}
readRDS(file = "../report/fig/figRewconn.rds")
```

## Exploratory Analyses
### Effect of mean and change in BMI
#### Whole brain analysis
##### BMI-only model
Next, we tested for significant effects of the average BMI and the individual change in BMI longitudinally across the three time points.
<!-- ### DMN -->
Using the images preprocessed with AROMA+CC, we found a significant negative association of average BMI and DMN connectivity in the lingual gyrus, mid orbital gyrus and temporal gyrus, which remained stable after including mFD as nuisance covariate (FWE cluster p<0.05). When using GSR preprocessed data, none of the clusters was significantly associated with average BMI (Table \@ref(tab:tableBMImodel).
```{r "BMIagesexPCCccavgBMIdeact",fig.cap="Negative association of average BMI and FC with PCC/precuneus in AROMA+CC preprocessed data", fig.subcap=c("adjusted for age and sex", "adjusted for age, sex and mFD"), fig.hold=TRUE, out.width = "50%"}
knitr::include_graphics(c("../report/BMIagesex_PCCcc_avgBMI_deact.pdf", "../report/BMIagesexfd_PCCcc_avgBMI_deact.pdf"))
```

@@

```{r "BMIagesexfd_PCCcc_avgBMI_deact", fig.cap="Negative association of average BMI and FC with PCC/precuneus in AROMA+CC preprocessed data, adjusted for BMI change, average mFD and change in mFD", fig.hold=TRUE, out.width = "85%"}
knitr::include_graphics("../report/fig/BMIagesexfd_PCCcc_avgBMI_deact.pdf")
```

```{r "BMIagesex_PCCcc_avgBMI_deact", fig.cap="Negative association of average BMI and FC with PCC/precuneus in AROMA+CC preprocessed data, adjusted for BMI change, average mFD and change in mFD", fig.hold=TRUE, out.width = "85%"}
knitr::include_graphics("../report/fig/BMIagesex_PCCcc_avgBMI_deact.pdf")
```

<!-- ### Reward -->
<!-- cc -->
For the reward network, we found a significant negative association of change in BMI with FC between NAcc and a cluster in the posterior-medial frontal region, i.e. supplementary motor area (see Table \@ref(tab:tableBMIFDmodel)). Voxel activation at local maximum within this cluster was significant at peak level after FWE-correction (p=$0.028$), also when evaluating the GSR corrected data (p=$0.038$).
```{r "BMIFDagesexNACCcccgnBMIdeact", fig.cap="Significant cluster with a negative Effect of change BMI on NAcc to posterior-medial frontal region, adjusted for age, sex, mean BMI, average mFD and change in mFD", fig.subcap=c("in AROMA+CC", "in AROMA+CC+GSR data"), out.width = "50%", fig.hold=TRUE, eval=TRUE}
knitr::include_graphics(c("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/BMIFDagesex_NACCcc_cngBMI_deact.pdf","/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/BMIFDagesex_NACCgsr_cngBMI_deact.pdf"))
```
Moreover, FC between the NAcc and one cluster in a more posterior region, i.e. motor cortex, was significantly positively related to average mFD. This result remained similar when using GSR corrected data.
```{r "BMIFDagesexNACCccavgFDact", fig.cap="Significant cluster with a positive Effect of average mFD on connectivity between NAcc and motor cortex, adjusted for age, sex, mean BMI, change in BMI and change in mFD", fig.subcap=c("in AROMA+CC", "in AROMA+CC+GSR data"), out.width = "50%", eval=TRUE}
knitr::include_graphics(c("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/BMIFDagesex_NACCcc_avgFD_act.pdf","/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/report/BMIFDagesex_NACCgsr_avgFD_act.pdf"))
```

@@

```{r "FDagesexNACCccavgFDact", fig.show = "hold", out.width = "50%", fig.cap="Positive association of mean mFD and FC of NAcc with cluster, adjusted for age, sex, mean BMI, change BMI and change mFD", fig.subcap=c("in AROMA+CC", "in AROMA+CC+GSR data")}
knitr::include_graphics("../report/FDagesex_NACCcc_avgFD_act.pdf")
knitr::include_graphics("../report/FDagesex_NACCgsr_avgFD_act.pdf")
```

@@

```{r tableBMIFDmodel}
# do not change chunk label as it corresponds to the manually defined (in table.R) table label
tab_BMIFDmodel <- readRDS(file = "../report/tab/FCTableList.rds")[[3]]
tab_BMIFDmodel
```
<!-- cc -->The effect of average BMI on connectivity between the PCC and other regions reported previously is confirmed. There is a significant association between average BMI and the connectivity between PCC and three other clusters. Results are detailed in Table \@ref(tab:tableBMIFDmodel).
Test statistics of these clusters differ only slightly from the effect found for average BMI when using mFD as nuisance covariate.
<!-- gsr -->As before, the effect did not survive when thresholding if the images had been GSR corrected.
```{r "BMIFDagesex_NACCcc_avgFD_act", out.width = "75%"}
knitr::include_graphics("../report/fig/BMIFDagesex_NACCcc_avgFD_act.pdf")
```

```{r "BMIFDagesex_NACCcc_cgnBMI_deact", out.width = "75%"}
knitr::include_graphics("../report/fig/BMIFDagesex_NACCcc_cngBMI_deact.pdf")
```

```{r "BMIFDagesex_NACCgsr_avgFD_act", out.width = "75%"}
knitr::include_graphics("../report/fig/BMIFDagesex_NACCgsr_avgFD_act.pdf")
```

```{r "BMIFDagesex_NACCgsr_cgnBMI_deact", out.width = "75%"}
knitr::include_graphics("../report/fig/BMIFDagesex_NACCgsr_cngBMI_deact.pdf")
```

>>>>

#### Functional Quality control
Resting state fMRI data quality control was performed according to the protocol by @Ciric_2018.
As the expected average head motion was high in this sample, it was difficult to determine an appropriate exclusion threshold which would not lead to the exclusion of a high number of individuals [@Beyer_2020]. Thus, we did not exclude any participants based on mean framewise displacement (FD) estimates beyond those who failed the anatomical preprocessing. We applied best-practice motion correction (ICA-AROMA and CC, plus optionally GSR) and monitored the reduction of motion-related artifact according to current recommendations [@Ciric_2018]. In addition, for models showing a significant time-by-group interaction, we performed a sensitivity analysis excluding the 10% data sets with highest mean FD (mFD).
```{r carpetplot, out.width="49%", out.height="30%", fig.cap="Carpet plot for quality control", fig.subcap=c("Example 1 with strong amount of structured noise", "Example 2 with less amount of structured noise"), fig.show='hold',fig.align='center', echo=FALSE}
carpets=c("../report/carpetplotadi006fu2.jpeg","../report/carpetplotadi16fu.jpeg")
knitr::include_graphics(carpets)
```
On the single-subject level, we used `plot_carpet` from `niworkflows.viz.plots` to generate carpet plots which depict denoising quality. Figure \@ref(fig:carpetplot) shows an exemplary carpet plot with (from top to bottom): percent outliers defined by AFNI, mFD, `OutlierCount`, DVARS (spatial root mean square of the data after temporal differencing),voxelwise timeseries from minimally preprocessed, AROMA non-aggressive and aggressive denoising, CC and CC + GSR data (red: GM voxels, green: WM voxels, blue: ventricle, green: cerebellum). All carpet plots were visually checked and if there was still structured noise in the CC+GSR-denoised functional data (such as black/white stripes, signal dropout), the participant was given a rating of 1 in `QA residuals`.
We evaluated mFD-FC relationships by computing a functional connectome based on [@Power_2012]. In more detail, we used the MNI coordinates of 246 cortical and subcortical spherical seed regions with 5mm radius in `NiftiSpheresMasker`, and calculated the Spearman rank correlation between these time series. Then, we correlated mean FD and QC values for each node across participants, and plotted the resulting mFD-FC correlation values in histogram (see Figure \@ref{exampleFC}. We reported the mFD-FC correlation per preprocessing scheme.
Further, we evaluated the distance-dependence of mFD-FC correlations by correlating the euclidean distance between nodes with the mFD-QC correlation and report mean, median and standard deviations of mFD, DVARS and number of outliers over all participants.

@@

@@

```{r figDvarsmFD, fig.align = "center", out.width="100%", fig.cap='Summary of quality measures DVARS and mFD', echo=FALSE}
figList <- readRDS(file = "../report/fig/figDvarsmFDList.rds")
(figList$fig1 | figList$fig2) / figList$fig3
```

@@

networks = c("../report/fig/DMN_thresholded_for_clusterFWE005.pdf",
             "../report/fig/Rew_thresholded_for_clusterFWE005.pdf")
knitr::include_graphics(networks)
tsnr <- "../report/tsnr.jpeg"
knitr::include_graphics(tsnr)
```

@@

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="40%",  eval=FALSE}
knitr::include_graphics(tsnr)
#readRDS(file = "../report/fig/fig_tSNR.rds")
```

@@

final_FC <- read.csv("../report/final_FC.csv")
```

```{r figaggDMN, fig.cap="DMN connectivity per group over time", out.width="75%", echo=FALSE}
fig_DMNconn<-readRDS(file = "../report/fig/figDMNconn.rds")
fig_DMNconn
```

```{r figaggRew,fig.cap="Reward network connectivity per group over time", out.width="75%", echo=FALSE}
fig_Rewconn<-readRDS(file = "../report/fig/figRewconn.rds")
fig_Rewconn
```

@@

@@

R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +  (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tp=anova(R1,R0)
```

```{qa check Rew model age,sex, echo=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

## Exploratory Analyses
### Effect of mean and change in BMI
#### Whole brain analysis
##### BMI-only model
Next, we tested for significant effects of the average BMI and the individual change in BMI longitudinally across the three time points.
<!-- ### DMN -->
Using the images preprocessed with AROMA+CC, we found a significant negative association of average BMI and DMN connectivity in the lingual gyrus, mid orbital gyrus and temporal gyrus, which remained stable after including mFD as nuisance covariate (FWE cluster p<0.05). When using GSR preprocessed data, none of the clusters was significantly associated with average BMI (Table \@ref(tab:tableBMImodel).
```{r "BMIagesexPCCccavgBMIdeact",fig.cap="Negative association of average BMI and FC with PCC/precuneus in AROMA+CC preprocessed data", fig.subcap=c("adjusted for age and sex", "adjusted for age, sex and mFD"), fig.hold=TRUE, out.width = "50%"}
knitr::include_graphics(c("../report/fig/BMIagesex_PCCcc_avgBMI_deact.pdf", "../report/fig/BMIagesexfd_PCCcc_avgBMI_deact.pdf"))
```

@@

<!-- ### Reward -->
<!-- cc -->
For the reward network, we found a significant negative association of change in BMI with FC between NAcc and a cluster in the posterior-medial frontal region, i.e. supplementary motor area (see Table \@ref(tab:tableBMIFDmodel)). Voxel activation at local maximum within this cluster was significant at peak level after FWE-correction (p=$0.028$), also when evaluating the GSR corrected data (p=$0.038$).
```{r "BMIFDagesexNACCcgnBMIdeact", fig.cap="Significant cluster with a negative Effect of change BMI on NAcc to posterior-medial frontal region, adjusted for age, sex, mean BMI and mFD", fig.subcap=c("in AROMA+CC", "in AROMA+CC+GSR data"), out.width = "50%", fig.hold=TRUE, eval=TRUE}
knitr::include_graphics(c("../report/fig/BMIFDagesex_NACCcc_cngBMI_deact.pdf",
                          "../report/fig/BMIFDagesex_NACCgsr_cngBMI_deact.pdf"))
```
Moreover, FC between the NAcc and one cluster in a more posterior region, i.e. motor cortex, was significantly positively related to average mFD. This result remained similar when using GSR corrected data.
```{r "BMIFDagesexNACCavgFDact", fig.cap="Significant cluster with a positive Effect of average mFD on connectivity between NAcc and motor cortex, adjusted for age, sex, mean BMI, change in BMI and change in mFD", fig.subcap=c("in AROMA+CC", "in AROMA+CC+GSR data"), out.width = "50%", eval=TRUE}
knitr::include_graphics(c("../report/fig/BMIFDagesex_NACCcc_avgFD_act.pdf",
                          "../report/fig/BMIFDagesex_NACCgsr_avgFD_act.pdf"))
```

@@

```{r "FDagesexNACCccavgFDact", fig.show = "hold", out.width = "50%", fig.cap="Positive association of mean mFD and FC of NAcc with cluster, adjusted for age, sex, mean BMI, change BMI and change mFD", fig.subcap=c("in AROMA+CC", "in AROMA+CC+GSR data")}
knitr::include_graphics("../report/fig/FDagesex_NACCcc_avgFD_act.pdf")
knitr::include_graphics("../report/fig/FDagesex_NACCgsr_avgFD_act.pdf")
```

@@

```{r tableBMIFDmodel}
# do not change chunk label as it corresponds to the manually defined (in table.R) table label
tab_BMIFDmodel <- readRDS(file = "../report/tab/FCTableList.rds")[[3]]
tab_BMIFDmodel
```
<!-- cc -->The effect of average BMI on connectivity between the PCC and other regions reported previously is confirmed. There is a significant association between average BMI and the connectivity between PCC and three other clusters. Results are detailed in Table \@ref(tab:tableBMIFDmodel).
Test statistics of these clusters differ only slightly from the effect found for average BMI when using mFD as nuisance covariate.
<!-- gsr -->As before, the effect did not survive when thresholding if the images had been GSR corrected.
```{r "BMIFDagesex_NACC_avgFD_act", fig.show = "hold", out.width = "50%", fig.cap="Positive association of mean mFD and FC of NAcc with cluster, adjusted for age, sex, average BMI, change BMI and change mFD", fig.subcap=c("in AROMA+CC", "in AROMA+CC+GSR data")}
knitr::include_graphics("../report/fig/BMIFDagesex_NACCcc_avgFD_act.pdf")
knitr::include_graphics("../report/fig/BMIFDagesex_NACCgsr_avgFD_act.pdf")
```

```{r "BMIFDagesex_NACC_cgnBMI_deact", fig.show = "hold", out.width = "50%", fig.cap="Positive association of change in BMI and FC of NAcc with cluster, adjusted for age, sex, average BMI, average mFD and change mFD", fig.subcap=c("in AROMA+CC", "in AROMA+CC+GSR data")}
knitr::include_graphics("../report/fig/BMIFDagesex_NACCcc_cngBMI_deact.pdf")
knitr::include_graphics("../report/fig/BMIFDagesex_NACCgsr_cngBMI_deact.pdf")
```
